`r params$project_title`

### 2021-03-16 reports/rmarkdown/01_data_pre_processing.Rmd
run on my computer update

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  #pdf_document:
    #toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  organisation: Karolinska Institutet
  pi_mail: prin.cipal@ki.se
  pi_name: Prin Cipal
  project_title: Broliden_5325
  redmine_issue: '#5325'
  requester_mail: kristina.broliden@ki.se
  requester_name: Kristina Broliden
  staff_mail: supp.ortstaff@nbis.se
  staff_name: Supp Ortstaff
  staff_web: https://nbis.se/about/staff/supp-ortstaff/
---

>>>>

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  organisation: Karolinska Institutet
  pi_mail: prin.cipal@ki.se
  pi_name: Prin Cipal
  project_title: Broliden_5325
  redmine_issue: '#5325'
  requester_mail: kristina.broliden@ki.se
  requester_name: Kristina Broliden
  staff_mail: supp.ortstaff@nbis.se
  staff_name: Supp Ortstaff
  staff_web: https://nbis.se/about/staff/supp-ortstaff/
---
